---
title: "Tutorial 1"
tutorial:
  version: 0.1
output:
  # html_document:
  learnr::tutorial:
    language: de
    # progressive: true
    allow_skip: true
    css: css/style.css
    # highlight: espresso
    # theme: cerulean
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
# library(studyr)
devtools::load_all()
knitr::opts_chunk$set(echo = FALSE)
gradethis::gradethis_setup(
  pass.praise = FALSE,
  fail.encourage = FALSE,
  pass = "Richtig!",
  fail = "Das ist leider falsch."
  )
tutorial_options(exercise.reveal_solution = TRUE)
```

<!-- <a href="https://meikesteinhilber.github.io/studyr/"> <i class="fa-solid fa-house" aria-label="Link zur studyr Homepage" aria-hidden="true"></i> </a> -->

<script>
$(document).ready(function() {
  $("#tutorial-topic").prepend(`<div class="img-right">
  <a href="https://meikesteinhilber.github.io/studyr/"> <i class="fa-solid fa-house" aria-label="Link zur studyr Homepage" aria-hidden="true"></i> 
  </a> 
  </div>`);
  
  $("a[href^='#']").on("click", function(event) {
    const currentSection = $(".section.current");
    var href = $(this).attr("href");
    
    if(!$(href, currentSection).length) {
      return;
    }
    var href = href.substr(1);
    event.preventDefault();
    
    const el = document.getElementById(href);
    if(!el) {
      return;
    }
    window.scrollTo({
      top: el.offsetTop,
      left: 0,
      behavior: "smooth",
    }); 
  });
});
</script>

## Nothing

## Test

<!-- <script> -->
<!-- alert("Hallo Welt!"); -->
<!-- </script> -->

<a href="#section-test-1">Test1</a>

<a href="#section-test-2">Test2</a>

<a href="#section-topic-1">Topik 1</a>

### Test1
X

X
X

X
X

X
X

X
X

X
X

X
X
X

### Test 2
X

X

X

X

X

X

X

X

X

X

X
X
X
X




## Topic 1

Test

```{r, child = "sub-tutorial-1.Rmd"}

```

## Topic 2

```{r, echo=FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r, context="server"}
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

## Topic 3

Quizfragen

```{r letter-a, echo=FALSE}
question("What number is the letter A in the English alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```

```{r letter-b, echo=FALSE}
question("What number is the letter A in the English alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```

## TOPIC 4 is a long a very long very very long long

```{r code-example, exercise=FALSE, echo=TRUE, eval=FALSE}
open_tutorial <- function(tutorial_name) {
  if (!is.character(tutorial)) {stop("Invalid input argument: tutorial name must be a charcter string.")}
  # learnr::run_tutorial(tutorial, package = "studyr")
}
NULL
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

```{r test-color, exercise=FALSE}
2+3
```

## Video

VIDEO

![](https://youtu.be/zNzZ1PfUDNk)

## Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

## Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
