---
title: "Tutorial 1"
tutorial:
  version: 0.1
output:
  learnr::tutorial:
    lanuage: de
    # progressive: true
    allow_skip: true
    css: css/style.css
    # highlight: espresso
    ace_theme: clouds
    # theme: united
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
# library(studyr)
knitr::opts_chunk$set(echo = FALSE, class.source="Rchunk", class.output="Rout")
```

<div class="img-right">
  <a href="https://meikesteinhilber.github.io/studyr/"> <i class="fa-solid fa-house" aria-label="Link zur studyr Homepage" aria-hidden="true"></i> 
  </a> 
</div>



<!-- <a href="https://meikesteinhilber.github.io/studyr/" class="button-link" target="_blank" rel="noopener noreferrer">Tutorial auf neuer Seite starten (empfohlen)</a></p> -->

## Topic 1
Test

```{r, child = "sub-tutorial-1.Rmd"}

```


## Topic 2

```{r, echo=FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r, context="server"}
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```



## Topic 3

Quizfragen

```{r letter-a, echo=FALSE}
question("What number is the letter A in the English alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```

```{r letter-b, echo=FALSE}
question("What number is the letter A in the English alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```



## TOPIC 4 is a long a very long very very long long

```{r code-example, exercise=FALSE, echo=TRUE, eval=FALSE}
open_tutorial <- function(tutorial_name) {
  if (!is.character(tutorial)) {stop("Invalid input argument: tutorial name must be a charcter string.")}
  # learnr::run_tutorial(tutorial, package = "studyr")
}
NULL
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

```{r test-color, exercise=FALSE}
2+3
```


## Video

VIDEO

![](https://youtu.be/zNzZ1PfUDNk)


## Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

## Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
